dynamics

### 2023-03-01 scripts/workshop/dynamics.Rmd
add reference

```{r}
ggplot()+
  geom_line(data=output_x1,mapping = aes(y=I,x=time, color=color_x))+
  scale_color_manual(name="",values = "black")+
  new_scale_color()+
  geom_line(data=output_x2, mapping=aes(y=I,x=time, color=color_x2))+
  scale_color_manual(name="",values = "red")+
  new_scale_color()+
  geom_line(output_x3, mapping=aes(y=I,x=time, color=color_x3))+
  scale_color_manual(name="",values = "orange")+
  new_scale_color()+
  geom_line(output_x4, mapping=aes(y=I,x=time, color=color_x4))+
  scale_color_manual(name="",values = "purple")+
  labs(y="N",x="Time")+
  ylim(0,40)+
  ggtitle(paste("Total Infected Individuals (2 Species) Over Time Across Varying Conditions w/o demo"))+
  theme_bw()
```

>>>>

```{r}
ggplot()+
  geom_line(data=output_x1,mapping = aes(y=I,x=time, color=color_x))+
  scale_color_manual(name="",values = "black")+
  new_scale_color()+
  geom_line(data=output_x2, mapping=aes(y=I,x=time, color=color_x2))+
  scale_color_manual(name="",values = "red")+
  new_scale_color()+
  geom_line(output_x3, mapping=aes(y=I,x=time, color=color_x3))+
  scale_color_manual(name="",values = "orange")+
  new_scale_color()+
  geom_line(output_x4, mapping=aes(y=I,x=time, color=color_x4))+
  scale_color_manual(name="",values = "purple")+
  new_scale_color()+
  geom_line(output_n1, mapping=aes(y=I,x=time, color=color_n))+
  scale_color_manual(name="",values = "forestgreen")+
  labs(y="N",x="Time")+
  ylim(0,40)+
  ggtitle(paste("Total Infected Individuals (2 Species) Over Time Across Varying Conditions w/o demo"))+
  theme_bw()
```

```{r}
ggplot()+
  geom_line(data=output_x1,mapping = aes(y=V,x=time, color=color_x))+
  scale_color_manual(name="",values = "black")+
  new_scale_color()+
  geom_line(data=output_x2, mapping=aes(y=V,x=time, color=color_x2))+
  scale_color_manual(name="",values = "red")+
  new_scale_color()+
  geom_line(output_x3, mapping=aes(y=V,x=time, color=color_x3))+
  scale_color_manual(name="",values = "orange")+
  new_scale_color()+
  geom_line(output_x4, mapping=aes(y=V,x=time, color=color_x4))+
  scale_color_manual(name="",values = "purple")+
  labs(y="N",x="Time")+
  ylim(0,75)+
  ggtitle(paste("Total Virions Over Time Across Varying Conditions w/o demo"))+
  theme_bw()
```
